---
title: "Homework 7"
author: "Peng Xu"
date: "10/24/2017"
output: html_notebook
---

```{r, include=FALSE}
library(foreach)
library(doParallel)
library(knitr)
Sys.setenv(LANG = "en")
knitr::opts_chunk$set(echo = TRUE)

```

# Question 2
```{r}
set.seed(12345)
y <- rnorm(n = 1e+07, mean = 1, sd = 1)
```

## Part a
for loop:
```{r}
system.time({
YMean <- mean(y)
SST <- 0
for(i in 1:length(y)){
    SST <- SST + (y[i]-YMean)^2
}
})
SST2
```

## Part b
vector operation:
```{r}
YMean <- mean(y)
perSS <- function(x){
    SS <- (x-YMean)^2
    return(SS)
}
system.time({
    result <- apply(as.matrix(y),MARGIN = 2,perSS)
    SST2 <- sum(result)
})
SST2
```

## Part c
dopar:
```{r}
registerDoParallel(cores = 2)
set.seed(12345)
y <- rnorm(n = 1e+07, mean = 1, sd = 1)
YMean <- mean(y)

system.time({
  Indivi <- foreach(b = 1:1e+07, .combine = "c") %dopar% {
    (y[b]-YMean)^2
  }
  SST <- sum(Indivi)
})

SST
stopImplicitCluster()

```

## Part d
parSapply:
```{r}
cl <- makeCluster(2)

set.seed(12345)
y <- rnorm(n = 1e+07, mean = 1, sd = 1)
YMean <- mean(y)


system.time({
  clusterExport(cl,"YMean")
  Indivi_2 <- parSapply(cl, 1:1e+07,
          function(x,y) {
            (y[x]-YMean)^2
            #return(SS)
            }, y)
})
SST <- sum(Indivi_2)
SST
stopCluster(cl)
```

# Question 3
In this problem, the step size $\alpha$ is not specified. So here the parallelization is used to find a value for $\alpha$. The results show that the differences between those choices are not significant. 
```{r}
set.seed(1256)
theta <- as.matrix(c(1, 2), nrow = 2)
X <- cbind(1, rep(1:10, 10))
h <- X %*% theta + rnorm(100, 0, 0.2)
```

```{r}
theta0_init <- 0
theta1_init <- 1
theta0_temp <- theta0_init
theta1_temp <- theta1_init
theta0_temp2 <- theta0_init
theta1_temp2 <- theta1_init
thres0 <- 0.0001  # the tolerance value
thres1 <- 0.0001
#alpha <- 0.05     # the step size
m <- length(h)
error0 <- 1
error1 <- 1

registerDoParallel(cores = 2)

  GDResult <- foreach(b = 1:10, .combine = "cbind") %dopar% {
    alpha <- b/1000+0.01
    while(error0 > thres0 | error1 > thres1){
      theta_temp <- as.matrix(c(theta0_temp, theta1_temp), nrow = 2)
      theta0_temp2 <- theta0_temp - alpha*sum(X %*% theta_temp - h)/m
      theta1_temp2 <- theta1_temp - alpha*sum((X %*% theta_temp - h)*X[,2])/m
      theta0_temp2
      theta1_temp2
      
      error0 <- abs(theta0_temp2 - theta0_temp)
      error1 <- abs(theta1_temp2 - theta1_temp)
      
      theta0_temp <- theta0_temp2
      theta1_temp <- theta1_temp2
    }
    return(c(theta0_temp2,theta1_temp2))
  }
  
stopImplicitCluster()
GDResult
```

```{r}
model <- lm(h~0+X)
summary(model)
```


# Question 4
## Part a
The parallelization method is used to repeat the bootstrap sampling process.
```{r}
set.seed(1267)
n <- 200
X <- 1/cbind(1, rt(n, df = 1), rt(n, df = 1), rt(n, df = 1))
beta <- c(1, 2, 3, 0)
Y <- X %*% beta + rnorm(100, sd = 3)
```

```{r}
List <- 1:200

#set.seed(123)
system.time({
  registerDoParallel(cores = 2)
  BootResult <- foreach(b = 1:10000,.combine = 'cbind') %dopar% {
    SampleSize <- 200
    Index <- sample(List, SampleSize, replace = TRUE)
    BootSample <- cbind(X[Index,],Y[Index])
    XBoot <- BootSample[,1:4]
    YBoot <- BootSample[,5]
  
    Beta_hat <- solve(t(XBoot)%*%XBoot)%*%t(XBoot)%*%YBoot
    Sigma <- 1/(SampleSize-4)*t(YBoot)%*%(diag(SampleSize)-XBoot%*%solve(t(XBoot)%*%XBoot)%*%t(XBoot))%*%YBoot
    Estimators <- rbind(Beta_hat,Sigma)
    return(Estimators)
  }
  stopImplicitCluster()
})
```

## Part b
```{r}

Mean <- apply(BootResult,MARGIN = 1, mean)
Var <- apply(BootResult, MARGIN = 1, var)

FinalResult <- data.frame(Mean = Mean, Var = Var)
rownames(FinalResult) <- c('Beta0','Beta1','Beta2','Beta3','Variance')
knitr::kable(FinalResult, caption="Estimators")

```

## Part c
```{r}
par(mfrow = c(2,2))
hist(BootResult[1,],breaks = 15, freq = FALSE, main = 'Hist of Beta0')
hist(BootResult[2,],breaks = 25, freq = FALSE, main = 'Hist of Beta1')
hist(BootResult[3,],breaks = 25, freq = FALSE, main = 'Hist of Beta2')
hist(BootResult[4,],breaks = 30, freq = FALSE, main = 'Hist of Beta3')
```







